Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2024-12-26 main.tex
fix estimate

        Let us write $\rho = \min(1,\varrho)$. 
        We define $y = - \rho \hat z_{S'}$ as vector in the opposite direction of $z_{S'}$ and with length $\rho$. 
        By construction, the closed line segment from $z_{S}$ to $y$ is contained in $\overline{\Ball_{\varrho}(z_S)}$,
        and we conclude that the convex closure of $T$ and $y$ must lie in $\patch_{\calT}(S)$.

@@

@@

            y 

@@

            - z_{S'}

@@

        The singular value $\sigma_{\max}(\Theta,G) \geq 1$ is monotonically increasing in $\tan(\beta)$ and must hence be the maximal singular value of $\Jacobian\Theta_{|G}$.
        Moreover, $\sigma_{\min}(\Theta,G) = \rho / \sigma_{\max}(\Theta,G) \leq \rho \leq 1$ must be the smallest singular value of $\Jacobian\Theta_{|G}$.

@@

        Recall that $G \in \calG$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
        Let $F_{z} \subseteq G$ be the face opposite to the vertex $z_{S'}$,
        which must be contained in some face of $T$. 
        Since $S'$ has dimension $n-\ell-1$, the vector $(n-\ell) h_{z}$ is the height vector of that face of $T$. 
        Thus, 
        \begin{align*}
            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
            = 
            \frac{ \vecnorm{ b_{z} } }{ (n-\ell)^{-1} \| (n-\ell) h_{z} \| }
            = 
            \frac{ \vecnorm{ z_{S'} } }{ (n-\ell)^{-1} \| (n-\ell) h_{z} \| }
            \leq 
            (n-\ell) \aspectratio(T)
%             = 
%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-\ell)^{-1} n \vol(T) }
%             \leq 
%             \frac{ n-\ell }{n!}
%             \cdot 
%             \frac{ \diam(T)^{n} }{ \vol(T) }
            .
        \end{align*}
        We abbreviate 
        \begin{align}\label{math:upper_bound_for_theta}
            \mu_{T,\ell} 
            := 
            \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} (n-\ell)^{2} \aspectratio(T)^{2} } 
            + 
            \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} (n-\ell)^{2} \aspectratio(T)^{2} }
            .
        \end{align}
        This establishes bounds on the singular values of the transformation. 
        In summary, the singular values of the Jacobian of $\Theta$ at almost every $x$ satisfy 
        \begin{align}
            \sigma_{1}(\Theta,x) \leq \mu_{T,\ell},
            \quad 
            \sigma_{2}(\Theta,x) = \dots = \sigma_{n-1}(\Theta) = 1,
            \quad 
            \sigma_{n}(\Theta,x)^{-1} \leq \mu_{T,\ell} / \rho.
        \end{align}

@@

>>>>

        \item 
        Let $\rho \in (0,1]$, yet to be determined. 
        We define $y = - \rho z_{S'}$ as vector in the opposite direction of $z_{S'}$ and with length $\rho \|z_{S'}\|$. 
        Henceforth, we assume $\rho \leq \varrho / \|z_{S'}\|$ so that $y \in \overline{\Ball_{\varrho}(z_S)}$.  
        By construction, the closed line segment from $z_{S}$ to $y$ is contained in $\overline{\Ball_{\varrho}(z_S)}$,
        and we conclude that the convex closure of $T$ and $y$ must lie in $\patch_{\calT}(S)$.

@@

        Let $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $G$,
        that is, the vector pointing to $z_{S'}$ and standing orthogonally on the affine hull of the face $G$ that opposes $z_{S'}$

@@

            \Theta_{|G}\left( z_{S'} \right) 

@@

            - \rho z_{S'} = y

@@

        The singular values $\sigma_{\max}(\Theta,G) \geq 1$ and $\sigma_{\min}(\Theta,G) \leq 1$ is monotonically increasing and decreasing, respectively, in $\tan(\beta)$. Hence they must the extremal maximal singular values of $\Jacobian\Theta_{|G}$.

@@

        Recall that $G \in \calG$ is obtained from $T$ via barycentric subdivisions: 
        first at $z_{S}$, leading to some intermediate $n$-simplex $T'$, and then at $z_{S'}$, leading to $G \subseteq T'$. 
        Let $F_{z} \subseteq G$ be the face opposite to the vertex $z_{S'}$, which is some face of $T'$.
        Now, the height of $F_{z}$ in $G$ is $(n-\ell)$-th of the height of $F_{z}$ in $T'$
        since $S'$ has dimension $n-\ell-1$. 
        The height of $F_{z}$ in $T'$ is just the height of the its opposing vertex, which lies in $S'$,
        and which equals the height of that vertex in $T$.
%         which must be contained in some face of $T$ containing $S$. 
%         The height vector $h_{z}$ is orthogonal to $F_{z}$. 
%         Since $S'$ has dimension $n-\ell-1$, the vector $(n-\ell) h_{z}$ is the height vector of that face of $T$,
%         pointing to some vertex of $S'$ and standing orthogonally on the face opposite to that vertex. 
        Thus, 
        \begin{align*}
            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
            = 
            \frac{ \vecnorm{ b_{z} } }{ (n-\ell)^{-1} \| (n-\ell) h_{z} \| }
            = 
            \frac{ \vecnorm{ z_{S'} } }{ (n-\ell)^{-1} \| (n-\ell) h_{z} \| }
            \leq 
            (n-\ell) \aspectratio(T)
%             = 
%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-\ell)^{-1} n \vol(T) }
%             \leq 
%             \frac{ n-\ell }{n!}
%             \cdot 
%             \frac{ \diam(T)^{n} }{ \vol(T) }
            .
        \end{align*}
        We abbreviate 
        \begin{align}\label{math:upper_bound_for_theta}
            \mu_{T,\ell} 
            := 
            \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} (n-\ell)^{2} \aspectratio(T)^{2} } 
            + 
            \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} (n-\ell)^{2} \aspectratio(T)^{2} }
            .
        \end{align}
        This establishes bounds on the singular values of the transformation. 
        In summary, the singular values of the Jacobian of $\Theta$ at almost every $x$ satisfy 
        \begin{align}
            \sigma_{1}(\Theta,x) \leq \mu_{T,\ell},
            \quad 
            \sigma_{2}(\Theta,x) = \dots = \sigma_{n-1}(\Theta) = 1,
            \quad 
            \sigma_{n}(\Theta,x)^{-1} = \frac{ \sigma_{1}(\Theta,x) }{ \left| \det \Jacobian\Theta_{|G} \right| } \leq \mu_{T,\ell} / \rho.
        \end{align}

@@

            \frac{ \sigma_{1}(\Phi,x) }{ \left| \det \Jacobian\Phi \right| }
